25 years of Social Work Research

### 2015-03-10 dataCleaning.Rmd
Updated.
Code update
Adds chunk to datacleaning.rmd that eliminates article records that do
not have a certain number of pages.

# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
```

@@

>>>>

# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
```

@@

```{r, comment=NA, echo=FALSE}

#Deletes article records associated with articles that are 3 pages or less  (this can be adjusted below in   ###                                                                               this chunk)

pages.df<-filter(full.df, attributes=="pages")
pages.df$record <- gsub("p", "", pages.df$record)
pages.df$record <- gsub("ArtID:\\s", "", pages.df$record)
pages.df$record<-gsub("S", "", pages.df$record)
pages.df$record <- gsub(" ", "", pages.df$record)

dashes<-filter(pages.df, grepl("-", record) )

splitDash<-strsplit(dashes$record, "-")
mat  <- matrix(unlist(splitDash), ncol=2, byrow=TRUE)
mat <- as.data.frame(mat)

mat$V1<- as.character(mat$V1)
mat$V2<- as.character(mat$V2)

mat$V1<- as.numeric(mat$V1)
mat$V2<- as.numeric(mat$V2)
mat <-mutate(mat, record=V2-V1)
mat<-select(mat, record)

dashes<-select(dashes, -record)
dashes.df<-cbind(dashes, mat)
dashes.ID<-dashes.df$articleID

pages.noDashes<-pages.df[!pages.df$articleID %in% dashes.ID, ]

pages.df<-rbind(pages.noDashes, dashes.df)
pages.df$record<-as.numeric(pages.df$record)
pages.df[is.na(pages.df)] <- 0

pages.remove<-filter(pages.df, record < 4)    ## Set threshold for retaining articles by number of pages
pages.remove.ID <- pages.remove$articleID

full.df <- full.df[!full.df$articleID %in% pages.remove.ID, ]
rownames(full.df) <- NULL
View(full.df)

rm(dashes, splitDash, mat, dashes.df, dashes.ID, pages.df, pages.noDashes)
